---
title: "CFA"
author: "Matt Dunham & Doug Whitaker"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = FALSE)
knitr::opts_chunk$set(warnings = FALSE)

# https://bookdown.org/yihui/rmarkdown-cookbook/font-color.html
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
            x)
  } else x
}

set.seed(1603)
```

```{r packages}
library("readxl")
library("MASDERtools")
library("ltm") # should be loaded by MASDERtools, but this gets rid of error: "Error in gauher("k") : object 'gh' not found"
library("lavaan")
library("semPlot")
library("semTools")
library("reshape2")
library("tidyverse")

set.seed(1603)

#data_scales_rta_imp <- read_excel("data/confidential/data_scales_rta_imp_2022-03-10.xlsx")
load("../data-cleaning/data/deidentified/s-somas_pilot2_data-rta-deidentified-20220310.Rdata")

```


# Acknowledgements

* This material is based upon work supported by the National Science Foundation under [Grant No. DUE-2013392](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2013392&HistoricalAwards=false).
* This analysis is based on work completed by the entire MASDER team. 
    * Some EFA code based on Matt Dunham's work

All analyses are performed in Microsoft Open R (Microsoft, 2020; R Core Team, 2020) with Intel MKL. The following packages were used:

* `MASDERtools` version `r packageVersion("MASDERtools")`, a custom package for these analyses, which explicitly imports the following packages (some of which should be cited):
    * IRT packages: `Gifi`, `ltm`, `mirt`
    * EFA packages: `networkD3` (Sankey diagrams)
    * Other formatting packages: `gridExtra`, `htmlwidgets`, `htmltools`
* IRT packages: `ltm`, which - despite being imported by `MASDERtools` - needs to be loaded in this analysis to avoid an error
* EFA packages: `nFactors`
* CFA packages: `lavaan`, `semPlot`, `semTools`
* Other analysis packages: `psych` (for reverse coding, identifying multivariate outliers, etc.)
* Other miscellaneous packages: `readxl` (for reading data), `kableExtra` (for colour-coding tables)

# Analysis

## CFA

### Full Model

Full Model, no HOF.

```{r cfa_prune_0}
cfa_string_prune_0 <- '
  Attain =~ Attain_1 + Attain_2 + Attain_3 + Attain_4 + Attain_5 + Attain_6 + Attain_7 + Attain_8 + Attain_9 + Attain_10 + Attain_11 + Attain_12 + Attain_13
  Cost =~ CostX_1 + + CostX_2 + CostX_3 + CostX_4 + CostX_5 + CostX_6 + CostX_7 + CostX_8 + CostX_9 + CostX_10 + CostX_11 + CostX_12 + CostX_13
  Difficulty =~ DifficultyX_1 + DifficultyX_2 + DifficultyX_3 + DifficultyX_4 + DifficultyX_5 + DifficultyX_6 + DifficultyX_7 + DifficultyX_8 + DifficultyX_9
  Goal =~ GoalX_1 + GoalX_2 + GoalX_3 + GoalX_4 + GoalX_5 + GoalX_6 + GoalX_7 + GoalX_8 + GoalX_9 + GoalX_10 + GoalX_11 + GoalX_12 + GoalX_13
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_4 + Expectancy_5 + Expectancy_6
  IntEnj =~ IntEnj_1 + IntEnj_2 + IntEnj_3 + IntEnj_4 + IntEnj_5 + IntEnj_6 + IntEnj_7 + IntEnj_8 + IntEnj_9
  Utility =~ Utility_1 + Utility_2 + Utility_3 + Utility_4 + Utility_5 + Utility_6 + Utility_7 + Utility_8 + Utility_9 + Utility_10 + Utility_11
  AcadSC =~ AcadSCX_1 + AcadSCX_2 + AcadSCX_3 + AcadSCX_4 +  AcadSCX_5 + AcadSCX_6 + AcadSCX_7 + AcadSCX_8 + AcadSCX_9 + AcadSCX_10 + AcadSCX_11 + AcadSCX_12 + AcadSCX_13 + AcadSCX_14
'
cfa_out_prune_0 <- lavaan::cfa(cfa_string_prune_0, data = data_scales_rta_imp, 
                           ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_0_res}
cat(cfa_string_prune_0)
lavaan::fitMeasures(cfa_out_prune_0, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_0)
#lavaan::modificationIndices(cfa_out_prune_0, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_0)

```


### Doug Drop Items

#### Round 1

```{r cfa_prune_1}
cfa_string_prune_1 <- '
  Attain =~ Attain_1 + Attain_2 +  Attain_5 + Attain_6 + Attain_7 +  Attain_9 + Attain_11 + Attain_12 + Attain_13
  TrueCost =~ CostX_1 + CostX_2 + CostX_5 + CostX_7 + CostX_10 + CostX_11 
  WorthIt =~ CostX_3 + CostX_4 + CostX_8 + CostX_9 + CostX_12 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_4 + DifficultyX_7 + DifficultyX_9
  LookSmart =~ GoalX_1 + GoalX_5 + GoalX_6 + GoalX_8 + GoalX_9
  FearEGO =~ GoalX_2 + GoalX_3 + GoalX_12 + GoalX_13 
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_3 + IntEnj_4 + IntEnj_6 + IntEnj_7 + IntEnj_8 + IntEnj_9
  Employment =~ Utility_1 + Utility_2 + Utility_4 + Utility_6 
  Personal =~ Utility_7 + Utility_8 + Utility_9 + Utility_10 
  Learn =~ AcadSCX_1 + AcadSCX_2 + AcadSCX_3 + AcadSCX_4 + AcadSCX_5 +AcadSCX_7 + AcadSCX_8 + AcadSCX_11 + AcadSCX_12
  SeekHelp =~  AcadSCX_6 + AcadSCX_9 + AcadSCX_13 + AcadSCX_14
  Cost =~ TrueCost + WorthIt
  GoalsX =~ LookSmart + FearEGO
  UtilityV =~ Employment + Personal
  AcadX =~ Learn + SeekHelp
'
cfa_out_prune_1 <- lavaan::cfa(cfa_string_prune_1, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_1_res}
cat(cfa_string_prune_1)
lavaan::fitMeasures(cfa_out_prune_1, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_1)
#lavaan::modificationIndices(cfa_out_prune_1, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_1)

```
Now we add in STV HOF.

```{r cfa_prune_2}
cfa_string_prune_2 <- '
  Attain =~ Attain_1 + Attain_2 +  Attain_5 + Attain_6 + Attain_7 +  Attain_9 + Attain_11 + Attain_12 + Attain_13
  TrueCost =~ CostX_1 + CostX_2 + CostX_5 + CostX_7 + CostX_10 + CostX_11 
  WorthIt =~ CostX_3 + CostX_4 + CostX_8 + CostX_9 + CostX_12 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_4 + DifficultyX_7 + DifficultyX_9
  LookSmart =~ GoalX_1 + GoalX_5 + GoalX_6 + GoalX_8 + GoalX_9
  FearEGO =~ GoalX_2 + GoalX_3 + GoalX_12 + GoalX_13 
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_3 + IntEnj_4 + IntEnj_6 + IntEnj_7 + IntEnj_8 + IntEnj_9
  Employment =~ Utility_1 + Utility_2 + Utility_4 + Utility_6 
  Personal =~ Utility_7 + Utility_8 + Utility_9 + Utility_10 
  Learn =~ AcadSCX_1 + AcadSCX_2 + AcadSCX_3 + AcadSCX_4 + AcadSCX_5 +AcadSCX_7 + AcadSCX_8 + AcadSCX_11 + AcadSCX_12
  SeekHelp =~  AcadSCX_6 + AcadSCX_9 + AcadSCX_13 + AcadSCX_14
  Cost =~ TrueCost + WorthIt
  GoalsX =~ LookSmart + FearEGO
  UtilityV =~ Employment + Personal
  AcadX =~ Learn + SeekHelp
  STV =~ UtilityV + Cost + Attain + IntEnj
'
cfa_out_prune_2 <- lavaan::cfa(cfa_string_prune_2, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_2_res}
cat(cfa_string_prune_2)
lavaan::fitMeasures(cfa_out_prune_2, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_2)
#lavaan::modificationIndices(cfa_out_prune_2, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_2)

```

Now we try to drop all HOF.

```{r cfa_prune_3}
cfa_string_prune_3 <- '
  Attain =~ Attain_1 + Attain_2 +  Attain_5 + Attain_6 + Attain_7 +  Attain_9 + Attain_11 + Attain_12 + Attain_13
  CostX =~ CostX_1 + CostX_2 + CostX_5 + CostX_7 + CostX_10 + CostX_11 + CostX_3 + CostX_4 + CostX_8 + CostX_9 + CostX_12 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_4 + DifficultyX_7 + DifficultyX_9
  GoalsX =~ GoalX_1 + GoalX_5 + GoalX_6 + GoalX_8 + GoalX_9 + GoalX_2 + GoalX_3 + GoalX_12 + GoalX_13 
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_3 + IntEnj_4 + IntEnj_6 + IntEnj_7 + IntEnj_8 + IntEnj_9
  Utility =~ Utility_1 + Utility_2 + Utility_4 + Utility_6 + Utility_7 + Utility_8 + Utility_9 + Utility_10 
  AcadSCX =~ AcadSCX_1 + AcadSCX_2 + AcadSCX_3 + AcadSCX_4 + AcadSCX_5 +AcadSCX_7 + AcadSCX_8 + AcadSCX_11 + AcadSCX_12 + AcadSCX_6 + AcadSCX_9 + AcadSCX_13 + AcadSCX_14
'
cfa_out_prune_3 <- lavaan::cfa(cfa_string_prune_3, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_3_res}
cat(cfa_string_prune_3)
lavaan::fitMeasures(cfa_out_prune_3, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_3)
#lavaan::modificationIndices(cfa_out_prune_3, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_3)

```

#### Round 2

```{r cfa_prune_4}
cfa_string_prune_4 <- '
  Attain =~ Attain_1 + Attain_5 + Attain_7 + Attain_11 + Attain_12 + Attain_13
  CostX =~ CostX_1 + CostX_2 +  CostX_3 + CostX_4 + CostX_5 + CostX_8 + CostX_9 + CostX_11 + CostX_12 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_4 + DifficultyX_7 + DifficultyX_9
  GoalsX =~ GoalX_2 + GoalX_3 + GoalX_5 + GoalX_8 + GoalX_9 + GoalX_12 
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_3 + IntEnj_4 + IntEnj_7 + IntEnj_8 + IntEnj_9
  Utility =~ Utility_1 + Utility_2 + Utility_4 + Utility_6 + Utility_7 + Utility_8 + Utility_9 + Utility_10 
  AcadSCX =~ AcadSCX_1 + AcadSCX_2 + AcadSCX_4 + AcadSCX_6 + AcadSCX_7 + AcadSCX_8 + AcadSCX_9 + AcadSCX_12 + AcadSCX_13
'
cfa_out_prune_4 <- lavaan::cfa(cfa_string_prune_4, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_4_res}
cat(cfa_string_prune_4)
lavaan::fitMeasures(cfa_out_prune_4, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_4)
#lavaan::modificationIndices(cfa_out_prune_4, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_4)

```

#### Round 3

Model converged and had decent fit measures. We need to push RMSEA lower and raise the reliability for Attainment (add items back in).

```{r cfa_prune_5}
cfa_string_prune_5 <- '
  Attain =~ Attain_1 + Attain_2 + Attain_5 + Attain_6 + Attain_7 + Attain_9 + Attain_11 + Attain_12 + Attain_13
  CostX =~ CostX_1 +  CostX_3 + CostX_4 + CostX_5 + CostX_8 + CostX_9 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_4 + DifficultyX_7 + DifficultyX_9
  GoalsX =~ GoalX_2 + GoalX_3 + GoalX_5 + GoalX_8 + GoalX_9 + GoalX_12 
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_3 + IntEnj_4 + IntEnj_7 + IntEnj_8
  Utility =~ Utility_4 + Utility_6 + Utility_7 + Utility_8 + Utility_9 + Utility_10 
  AcadSCX =~ AcadSCX_1 + AcadSCX_2 + AcadSCX_4 + AcadSCX_6 + AcadSCX_7 + AcadSCX_8 + AcadSCX_9 + AcadSCX_12
'
cfa_out_prune_5 <- lavaan::cfa(cfa_string_prune_5, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_5_res}
cat(cfa_string_prune_5)
lavaan::fitMeasures(cfa_out_prune_5, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_5)
#lavaan::modificationIndices(cfa_out_prune_5, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_5)

```


```{r cfa_prune_6}
cfa_string_prune_6 <- '
  Attain =~ Attain_1 + Attain_2 + Attain_5 + Attain_6 + Attain_7 + Attain_9 + Attain_11 + Attain_12 + Attain_13
  CostX =~ CostX_1 +  CostX_3 + CostX_4 + CostX_5 + CostX_8 + CostX_9 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_4 + DifficultyX_7 + DifficultyX_9
  GoalsX =~ GoalX_2 + GoalX_3 + GoalX_5 + GoalX_8 + GoalX_9 + GoalX_12 
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_3 + IntEnj_4 + IntEnj_7 + IntEnj_8
  Utility =~ Utility_4 + Utility_6 + Utility_7 + Utility_8 + Utility_9 + Utility_10 
  AcadSCX =~ AcadSCX_1 + AcadSCX_2 + AcadSCX_4 + AcadSCX_6 + AcadSCX_7 + AcadSCX_8 + AcadSCX_9 + AcadSCX_12
  STV =~ Attain + IntEnj + Utility + CostX
'
cfa_out_prune_6 <- lavaan::cfa(cfa_string_prune_6, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_6_res}
cat(cfa_string_prune_6)
lavaan::fitMeasures(cfa_out_prune_6, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_6)
#lavaan::modificationIndices(cfa_out_prune_6, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_6)

```

#### Round 4

Things are looking good. All alpha and omega reliabilities above 0.70, CFI & TLI > 0.95, SRMR is still above 0.05 but below 0.08, RMSEA is just above 0.08 (get down to 0.06/0.07.)

```{r cfa_prune_7}
cfa_string_prune_7 <- '
  Attain =~ Attain_1 + Attain_2 + Attain_5 + Attain_6 + Attain_7 + Attain_11 + Attain_12 + Attain_13
  CostX =~ CostX_1 +  CostX_3 + CostX_4 + CostX_8 + CostX_9 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_4 + DifficultyX_7 + DifficultyX_9
  GoalsX =~ GoalX_2 + GoalX_3 + GoalX_5 + GoalX_8 + GoalX_9
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_3 + IntEnj_4 + IntEnj_7 + IntEnj_8
  Utility =~ Utility_4 + Utility_6 + Utility_7 + Utility_8 + Utility_9 + Utility_10 
  AcadSCX =~ AcadSCX_2 + AcadSCX_4 + AcadSCX_6 + AcadSCX_7 + AcadSCX_8 + AcadSCX_9 + AcadSCX_12
  STV =~ Attain + IntEnj + Utility + CostX
'
cfa_out_prune_7 <- lavaan::cfa(cfa_string_prune_7, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_7_res}
cat(cfa_string_prune_7)
lavaan::fitMeasures(cfa_out_prune_7, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_7)
semTools::reliabilityL2(cfa_out_prune_7, "Difficulty")
semTools::reliabilityL2(cfa_out_prune_7, "Expectancy")
semTools::reliabilityL2(cfa_out_prune_7, "GoalsX")
semTools::reliabilityL2(cfa_out_prune_7, "AcadSCX")

#lavaan::modificationIndices(cfa_out_prune_7, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_7)

```

Drop GoalX and see what happens...

```{r cfa_prune_8}
cfa_string_prune_8 <- '
  Attain =~ Attain_1 + Attain_2 + Attain_5 + Attain_6 + Attain_7 + Attain_11 + Attain_12 + Attain_13
  CostX =~ CostX_1 +  CostX_3 + CostX_4 + CostX_8 + CostX_9 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_4 + DifficultyX_7 + DifficultyX_9
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_3 + IntEnj_4 + IntEnj_7 + IntEnj_8
  Utility =~ Utility_4 + Utility_6 + Utility_7 + Utility_8 + Utility_9 + Utility_10 
  AcadSCX =~ AcadSCX_2 + AcadSCX_4 + AcadSCX_6 + AcadSCX_7 + AcadSCX_8 + AcadSCX_9 + AcadSCX_12
  STV =~ Attain + IntEnj + Utility + CostX
'
cfa_out_prune_8 <- lavaan::cfa(cfa_string_prune_8, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_8_res}
cat(cfa_string_prune_8)
lavaan::fitMeasures(cfa_out_prune_8, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_8)
semTools::reliabilityL2(cfa_out_prune_8, "Difficulty")
semTools::reliabilityL2(cfa_out_prune_8, "Expectancy")
#semTools::reliabilityL2(cfa_out_prune_8, "GoalsX")
semTools::reliabilityL2(cfa_out_prune_8, "AcadSCX")

#lavaan::modificationIndices(cfa_out_prune_8, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_8)

```

Go back to Prune 7 and drop STV HOF.

```{r cfa_prune_9}
cfa_string_prune_9 <- '
  Attain =~ Attain_1 + Attain_2 + Attain_5 + Attain_6 + Attain_7 + Attain_11 + Attain_12 + Attain_13
  CostX =~ CostX_1 +  CostX_3 + CostX_4 + CostX_8 + CostX_9 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_4 + DifficultyX_7 + DifficultyX_9
  GoalsX =~ GoalX_2 + GoalX_3 + GoalX_5 + GoalX_8 + GoalX_9 
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_3 + IntEnj_4 + IntEnj_7 + IntEnj_8
  Utility =~ Utility_4 + Utility_6 + Utility_7 + Utility_8 + Utility_9 + Utility_10 
  AcadSCX =~ AcadSCX_2 + AcadSCX_4 + AcadSCX_6 + AcadSCX_7 + AcadSCX_8 + AcadSCX_9 + AcadSCX_12
'
cfa_out_prune_9 <- lavaan::cfa(cfa_string_prune_9, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_9_res}
cat(cfa_string_prune_9)
lavaan::fitMeasures(cfa_out_prune_9, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_9)

#lavaan::modificationIndices(cfa_out_prune_9, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_9)

```

#### Round 5

Fit statistics decent, try to raise reliability of GoalsX.

Start modifying Prune 9.

```{r cfa_prune_10}
cfa_string_prune_10 <- '
  Attain =~ Attain_1 + Attain_2 + Attain_5 + Attain_6 + Attain_7 + Attain_11 + Attain_12 + Attain_13
  CostX =~ CostX_1 +  CostX_3 + CostX_4 + CostX_8 + CostX_9 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_7 + DifficultyX_9
  GoalsX =~ GoalX_2 + GoalX_3 + GoalX_5 + GoalX_6 + GoalX_8 + GoalX_9 
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_4 + IntEnj_7 + IntEnj_8
  Utility =~ Utility_4 + Utility_6 + Utility_7 + Utility_8 + Utility_9 + Utility_10 
  AcadSCX =~ AcadSCX_2 + AcadSCX_4 + AcadSCX_6 + AcadSCX_7 + AcadSCX_8 + AcadSCX_9 + AcadSCX_12
'
cfa_out_prune_10 <- lavaan::cfa(cfa_string_prune_10, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_10_res}
cat(cfa_string_prune_10)
lavaan::fitMeasures(cfa_out_prune_10, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_10)

#lavaan::modificationIndices(cfa_out_prune_10, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_10)

```

```{r cfa_prune_11}
cfa_string_prune_11 <- '
  Attain =~ Attain_1 + Attain_2 + Attain_5 + Attain_6 + Attain_7 + Attain_11 + Attain_12 + Attain_13
  CostX =~ CostX_1 +  CostX_3 + CostX_4 + CostX_8 + CostX_9 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_7 + DifficultyX_9
  GoalsX =~ GoalX_2 + GoalX_3 + GoalX_5 + GoalX_6 + GoalX_8 + GoalX_9 
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_4 + IntEnj_7 + IntEnj_8
  Utility =~ Utility_4 + Utility_6 + Utility_7 + Utility_8 + Utility_9 + Utility_10 
  AcadSCX =~ AcadSCX_2 + AcadSCX_4 + AcadSCX_6 + AcadSCX_7 + AcadSCX_8 + AcadSCX_9 + AcadSCX_12
  STV =~ Attain + IntEnj + Utility + CostX
'
cfa_out_prune_11 <- lavaan::cfa(cfa_string_prune_11, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_11_res}
cat(cfa_string_prune_11)
lavaan::fitMeasures(cfa_out_prune_11, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_11)
semTools::reliabilityL2(cfa_out_prune_11, "Difficulty")
semTools::reliabilityL2(cfa_out_prune_11, "Expectancy")
semTools::reliabilityL2(cfa_out_prune_11, "GoalsX")
semTools::reliabilityL2(cfa_out_prune_11, "AcadSCX")
#lavaan::modificationIndices(cfa_out_prune_11, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_11)

```

Now drop GoalsX from Prune 11.

```{r cfa_prune_12}
cfa_string_prune_12 <- '
  Attain =~ Attain_1 + Attain_2 + Attain_5 + Attain_6 + Attain_7 + Attain_11 + Attain_12 + Attain_13
  CostX =~ CostX_1 +  CostX_3 + CostX_4 + CostX_8 + CostX_9 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_7 + DifficultyX_9
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_4 + IntEnj_7 + IntEnj_8
  Utility =~ Utility_4 + Utility_6 + Utility_7 + Utility_8 + Utility_9 + Utility_10 
  AcadSCX =~ AcadSCX_2 + AcadSCX_4 + AcadSCX_6 + AcadSCX_7 + AcadSCX_8 + AcadSCX_9 + AcadSCX_12
  STV =~ Attain + IntEnj + Utility + CostX
'
cfa_out_prune_12 <- lavaan::cfa(cfa_string_prune_12, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_12_res}
cat(cfa_string_prune_12)
lavaan::fitMeasures(cfa_out_prune_12, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_12)
semTools::reliabilityL2(cfa_out_prune_12, "Difficulty")
semTools::reliabilityL2(cfa_out_prune_12, "Expectancy")
#semTools::reliabilityL2(cfa_out_prune_12, "GoalsX")
semTools::reliabilityL2(cfa_out_prune_12, "AcadSCX")
#lavaan::modificationIndices(cfa_out_prune_12, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_12)

```

Now drop HOF from Prune 12.

```{r cfa_prune_13}
cfa_string_prune_13 <- '
  Attain =~ Attain_1 + Attain_2 + Attain_5 + Attain_6 + Attain_7 + Attain_11 + Attain_12 + Attain_13
  CostX =~ CostX_1 +  CostX_3 + CostX_4 + CostX_8 + CostX_9 + CostX_13
  Difficulty =~ DifficultyX_2 + DifficultyX_3 + DifficultyX_7 + DifficultyX_9
  Expectancy =~ Expectancy_1 + Expectancy_2 + Expectancy_3 + Expectancy_6
  IntEnj =~ IntEnj_2 + IntEnj_4 + IntEnj_7 + IntEnj_8
  Utility =~ Utility_4 + Utility_6 + Utility_7 + Utility_8 + Utility_9 + Utility_10 
  AcadSCX =~ AcadSCX_2 + AcadSCX_4 + AcadSCX_6 + AcadSCX_7 + AcadSCX_8 + AcadSCX_9 + AcadSCX_12
'
cfa_out_prune_13 <- lavaan::cfa(cfa_string_prune_13, data = data_scales_rta_imp, 
                               ordered = names(data_scales_rta_imp))
```
```{r cfa_prune_13_res}
cat(cfa_string_prune_13)
lavaan::fitMeasures(cfa_out_prune_13, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea.ci.lower", "rmsea", "rmsea.ci.upper", "srmr"))
semTools::reliability(cfa_out_prune_13)
# semTools::reliabilityL2(cfa_out_prune_13, "Difficulty")
# semTools::reliabilityL2(cfa_out_prune_13, "Expectancy")
# #semTools::reliabilityL2(cfa_out_prune_13, "GoalsX")
# semTools::reliabilityL2(cfa_out_prune_13, "AcadSCX")
#lavaan::modificationIndices(cfa_out_prune_13, sort = TRUE, maximum.number = 20)
#semPlot::semPaths(cfa_out_prune_13)

```