---
title: "S-SOMAS Pilot 2 (Fall 2021) Analysis"
author: "Douglas Whitaker"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = FALSE)

# https://bookdown.org/yihui/rmarkdown-cookbook/font-color.html
colorize <- function(x, color = "red") {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
            x)
  } else x
}

set.seed(1456)
```

```{r packages}
library("readxl")
library("MASDERtools")
library("ltm") # should be loaded by MASDERtools, but this gets rid of error: "Error in gauher("k") : object 'gh' not found"
library("lavaan")
library("semPlot") 
library("kableExtra")
library("psych")
library("semPlot")
library("semTools")
library("nFactors")
library("ids")
library("WrightMap")
library("ggplot2")
library("reshape2")
library("RColorBrewer")
```

# Note about Preliminary Analyses

`r colorize("<strong>Please note that all analyses detailed herein are <em>preliminary</em> and subject to change.</strong>", "Tomato")`

# Acknowledgements

* This material is based upon work supported by the National Science Foundation under [Grant No. DUE-2013392](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2013392&HistoricalAwards=false).
* This analysis is based on work completed by the entire MASDER team. 
    * Some EFA code based on Matt Dunham's work

All analyses are performed in Microsoft Open R (Microsoft, 2020; R Core Team, 2020) with Intel MKL. The following packages were used:

* `MASDERtools` version `r packageVersion("MASDERtools")`, a custom package for these analyses, which explicitly imports the following packages (some of which should be cited):
    * IRT packages: `Gifi`, `ltm`, `mirt`
    * EFA packages: `networkD3` (Sankey diagrams)
    * Other formatting packages: `gridExtra`, `htmlwidgets`, `htmltools`
* IRT packages: `ltm`, which - despite being imported by `MASDERtools` - needs to be loaded in this analysis to avoid an error
* EFA packages: `nFactors`
* CFA packages: `lavaan`, `semPlot`, `semTools`
* Other analysis packages: `psych` (for reverse coding, identifying multivariate outliers, etc.)
* Other miscellaneous packages: `readxl` (for reading data), `kableExtra` (for colour-coding tables)

# Analysis

## Reading and Cleaning Data

The file `01 Data Cleaning (Run First).Rmd` handles reading and cleaning the data.

```{r readdata}
load("../data-cleaning/data/deidentified/s-somas_pilot2_data-rta-deidentified-20220310.Rdata")
```

## Item Response Theory

### Dimensionality

First, we need to assess the dimensionality of each scale; we need each scale to be unidimensional. Before this can be done, we need to determine if treating the response scale should be treated as linear or ordinal.

```{r princaller_res1}
print(MASDERtools::princaller(dat = data_scales_rta, scale.names = scale_names, method = "both"))
```

Based on the loss functions, the results are similar for a linear and an ordinal approach are similar. Therefore the linear approach is used (more parsimonious).

```{r princaller_res3, fig.show = "hold", out.width = "50%"}
MASDERtools::princaller(dat = data_scales_rta, scale.names = scale_names, method = "linear")
```


#### Summary of Dimensionality 

The following items do not load with the others:

* Pilot 2 (Fall 2021)
    * Attain: {4}, {others}
    * CostX: {1, 10}, {2, 5, 7, 11}, and {others}
    * DifficultyX: {5}, {1, 6, 8}, {2, 3, 4, 7, 9}
    * GoalX: {4}, {10, 11}, {2, 3, 12, 13}, {1, 5, 6, 7, 8, 9}
    * Expectancy: {5}, {1, 2, 3, 4, 6}
    * IntEnj: {1, 3, 5, 6, 9}, {2, 4, 7, 8}
    * Utility: {7, 8, 9, 10, 11}, {1, 2, 3, 4, 5, 6}
    * AcadSCX: {10}, {6, 9, 13, 14}, {others}
  
Based on examining the above graphs and the item text, we determine sets of items to drop.

```{r dropitemslists, echo = TRUE, cache = FALSE}
drop_items_a <- list(c(4), # Attain
                     c(1, 10), # CostX
                     c(1, 6, 8, 5), # DifficultyX
                     c(4, 10, 11), # GoalX
                     c(5), # Expectancy
                     c(NULL), # IntEnj
                     c(NULL), # Utility
                     c(10, 6, 9, 13, 14)) # AcadSCX

drop_items_b <- list(c(4, 8, 3, 10), # Attain
                     c(1, 10), # CostX
                     c(1, 6, 8, 5), # DifficultyX
                     c(4, 10, 11), # GoalX
                     c(5), # Expectancy
                     c(NULL), # IntEnj
                     c(NULL), # Utility
                     c(10, 6, 9, 13, 14)) # AcadSCX
```
    
These items should be investigated for inclusion/exclusion further. 

### Polytomous IRT modeling

IRT is a framework for analyzing categorical data, including polytomous responses such as to Likert-type items. IRT analyses presume unidimensional scales (except in multidimensional IRT); the dimensionality analysis conducted above suggests that there are reasonably unidimensional sets of items to examine. Three models will be considered:

* Partial Credit Model (PCM; PCM)
* Generalized Partial Credit Model (GPCM; GPCM)
* Graded Response Model (GRM; GRM)

All three models are appropriate for polytomous responses such as those from the S-SOMAS scales (e.g., @Mair2018).

`r colorize("In the future, multivariate IRT models should be considered.", "DodgerBlue")`

The `ltm` package (Rizopoulos, 2006) is used in the model comparison analysis; the `mirt` package (Chalmers, 2012) is used for the other IRT analyses. Both packages are accessed through the `MASDERtools` package.

Not all items have responses in each category, which is a requirement to run IRT. We will drop these items now. Future data collection may result in changing this. 

```{r comparer_scratch} 
which(apply(data_scales_rta, MARGIN = 2, FUN = function(x){length(table(x))}) != 7)
```

`r colorize("Note: The following block of code takes a LONG time to run.")`

```{r comparer_res1}

comparer_out_1 <- MASDERtools::comparer(dat = data_scales_rta, 
                                        scale.names = scale_names)

```

We now examine GRM results using all items.

```{r grmer_1, fig.show = "hold", out.width = "33%"}
grmit_out_1 <- MASDERtools::grmit(dat = data_scales_rta, scale.names = scale_names)
itemfit_out1 <- MASDERtools::itemfitbuilder(grmit_out_1)
MASDERtools::itemplotter(grmit_out_1)
``` 


```{r item_fit_graphs1}
MASDERtools::item_fit_plotter(grmit_out_1)
```

[More resources for item plots.](https://aidenloe.github.io/irtplots.html)

```{r grmer_1_tabs}
itemfit_out1 %>% 
  kbl() %>%
  kable_paper("hover", full_width = FALSE) %>% 
  column_spec(2:3, color = "white", background = ifelse(abs(itemfit_out1$z.outfit) > 2, "Tomato", "DodgerBlue")) %>%
  column_spec(4:5, color = "white", background = ifelse(abs(itemfit_out1$z.infit) > 2, "Tomato", "DodgerBlue")) 
```

Now we drop the first set of items.

```{r grmer_2, fig.show = "hold", out.width = "33%"}
grmit_out_2 <- MASDERtools::grmit(dat = data_scales_rta, scale.names = scale_names,
                                  drop.items = drop_items_a)
itemfit_out2 <- MASDERtools::itemfitbuilder(grmit_out_2)
MASDERtools::itemplotter(grmit_out_2)
``` 


```{r item_fit_graphs2}
MASDERtools::item_fit_plotter(grmit_out_2)
```

```{r grmer_2_tabs}
itemfit_out2 %>% 
  kbl() %>%
  kable_paper("hover", full_width = FALSE) %>% 
  column_spec(2:3, color = "white", background = ifelse(abs(itemfit_out2$z.outfit) > 2, "Tomato", "DodgerBlue")) %>%
  column_spec(4:5, color = "white", background = ifelse(abs(itemfit_out2$z.infit) > 2, "Tomato", "DodgerBlue")) 
```
Decisions about item misfit need to be made. [This paper by Köhler and Hartig (2017) might be helpful for determining practical significance.](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5978672/)

We run more GRM models here.

```{r grmer_3, fig.show = "hold", out.width = "33%", cache = FALSE}
grmit_out_3 <- MASDERtools::grmit(dat = data_scales_rta, scale.names = scale_names,
                                  drop.items = drop_items_b)
# itemfit_out2 <- MASDERtools::itemfitbuilder(grmit_out_2)
# MASDERtools::itemplotter(grmit_out_2)
``` 


### Wright Maps

```{r wrighter}
wrighter <- function(grmit_out, 
                     scale_names, 
                     scale_names_print = NULL, 
                     thresh_symbols = 49:54,
                     colors_item = "Dark2",
                     colors_scales = "Set1"){
  if (is.null(scale_names_print)){
    scale_names_print <- scale_names
  }
  for (i in 1:length(scale_names)){
    tmp_item_symbols <- matrix(rep(thresh_symbols, 
                                     times = nrow(unimirt::ThurstonianThresh(
                                       grmit_out[[i]]$mirt.out))),
                                 byrow = TRUE, 
                                 ncol = (ncol(unimirt::ThurstonianThresh(
                                                grmit_out[[i]]$mirt.out)))-1)
    tmp_item_colours <- matrix(rep(RColorBrewer::brewer.pal(
                                     length(thresh_symbols), colors_item), 
                                 times = nrow(unimirt::ThurstonianThresh(
                                      grmit_out[[i]]$mirt.out))),
                                 byrow = TRUE, 
                                 ncol = (ncol(unimirt::ThurstonianThresh(
                                                grmit_out[[i]]$mirt.out)))-1)
    tmp_thresh <- unimirt::ThurstonianThresh(grmit_out[[i]]$mirt.out)
    WrightMap::wrightMap(thetas = grmit_out[[i]]$personscores,
                         thresholds = tmp_thresh[,-1],
                         main.title = paste(
                           "Wright Map with Thurstonian Thresholds for ", 
                           scale_names_print[i], sep = ""),
                         label.items = tmp_thresh[,1],
                         show.thr.lab = FALSE,
                         thr.sym.pch = tmp_item_symbols,
                         thr.sym.cex = 1.5,
                         thr.sym.col.fg = tmp_item_colours,
                         dim.color = RColorBrewer::brewer.pal(
                           length(scale_names), colors_scales)[i])
  }
}
```

Here are the Wright Maps for the GRM results with all items.
```{r wright1}
wrighter(grmit_out = grmit_out_1, scale_names = scale_names, scale_names_print = scale_names_print)
```

Here are the Wright Maps for the GRM results with set "A" dropped.
```{r wright2}
wrighter(grmit_out = grmit_out_2, scale_names = scale_names, scale_names_print = scale_names_print)
```

Here are the Wright Maps for the GRM results with set "B" dropped.
```{r wright3, cache = FALSE}
wrighter(grmit_out = grmit_out_3, scale_names = scale_names, scale_names_print = scale_names_print)
```